\begin{recipe}{Pilafi / Pilaf / Pilau}{Serves 2}{40 minutes}
\freeform This is a Turkish-inspired variant of a common middle eastern dish; this is a personal adaptation of a recipe I grew up with as a child that my yaya would cook
\freeform Spice quantities are estimates and should be used to taste, they resemble average ratios I personally use at an estimated quantity

\Ing{1 Brown onion (can use half if preferred)}
\Ing{3 cloves of Garlic}
Finely chop the onion and garlic, and set aside in a small dish

\Ing{2 tbsp of Butter}
Melt the butter in a saucepan over high heat, until the butter starts to brown. Once browning, pour in the onion and garlic and stir for 1 minute or until fragrant

\Ing{0.5 tbsp of Turmeric}
\Ing{1 tbsp of Cumin}
\Ing{1 tbsp of Smoked Paprika}
\Ing{4 Bay leaves}
\Ing{1 cup Basmati rice}
Add spices and rice to the pot and stir until mixed thoroughly, taking care not to break the bay leaves. Leave to cook for 1 minute

\Ing{1 cup of Chicken stock}
Pour in the chicken stock and stir until rice is evenly distributed in the pot. Once near a boil, place the lid on the saucepan and switch to a low heat. Leave to cook for 20 minutes

\newstep
Turn off the heat, remove the lid from the pot, and stir to fluff the rice. Leave to sit for 5 minutes then serve after removing the bay leaves



\freeform The following is an optional side that can be served with the pilafi. The chicken can be replaced with vegetarian alternatives.

\Ing{2 Chicken thigh fillets}
Cut the chicken into small 2cm cubes or similar, and place into a mixing bowl

\Ing{0.25 cups of Mayonnaise (or enough to coat). Greek Yoghurt can be used alternatively}
\Ing{1 tbsp of Cumin}
\Ing{1 tbsp of Smoked Paprika}
\Ing{0.25 tbsp of Oregano}
\Ing{0.25 tbsp of Cardamom (Powder)}
\Ing{0.25 tbsp of Cloves}
Add the mayo and spices to the bowl, then evenly coat the chicken with the mixture

\Ing{Oil (Olive preferred)}
In a large fry pan, heat the oil and add the chicken. Cook while turning the chicken frequently until the chicken is well cooked. Estimate ~15 minutes.

\newstep
Remove from the pan, and place on-top of the plated pilaf

\end{recipe}
